---
title: "Arimax forecast using quantity and quantity in promotion"
output: arimax_notebook
---







```{r}

#arimax_fit <- auto.arima(train, xreg = promo_train, approximation=FALSE , stepwise=FALSE)
arimax_fit <- auto.arima(train, xreg = promo_dummy1)
```


```{r}

#arimax_fit <- auto.arima(train, xreg = promo_train, approximation=FALSE , stepwise=FALSE)
arimax_fit <- auto.arima(train_year, xreg = dummies_year)
```


```{r}
ano1 <-  0
ano2 <- (-1/2)
plot_start <- 0 + ( 365 * ano1)
plot_end <- 365 + ( 365 * ano2)
autoplot(ts(train[plot_start:plot_end]), series='train') +
  autolayer(ts(fitted(arimax_fit)[plot_start:plot_end]),  series="fitted") +  
  xlab("day") +
  ylab("quantity") +
  ggtitle("Comparaçao de fitted com treino") +
  guides(colour=guide_legend(title="Legend"))
```



```{r}
#Residuals, accuracy e modelo
checkresiduals(arimax_fit)
accuracy(arimax_fit)
arimax_fit
```


```



```{r}


arimax_fit2 <- auto.arima(train_year, xreg = xreg)
```


```{r}
arimax_fit2
```

```{r}
accuracy(arimax_fit2)
```



```{r}
checkresiduals(arimax_zero_values)
```

```{r}
result_arimax_zero_values <- forecast(arimax_zero_values, xreg=c(1), h = 1)
```


```{r}
result_arimax_zero_values
```

```{r}
accuracy(test,result_arimax_zero_values)
```


```{r}
plot_start = 0
plot_end = 1
autoplot(test, series='train') +
  autolayer(window(result_arimax_zero_values, start=105 + 2/7, end=113 + 4/7, frequency = 7),   series="forecasted") +
  xlab("day") +
  ylab("quantity") +
  ggtitle("Quantity of fresh fish seleed") +
  guides(colour=guide_legend(title="Legend"))
```


```{r}
plot_start = 0
plot_end = 30
autoplot(test, series='train') +
  autolayer(ts(fitted(arimax_fit_raw)[plot_start:plot_end]),  series="fitted") +
  xlab("day") +
  ylab("quantity") +
  ggtitle("Quantity of fresh fish seleed") +
  guides(colour=guide_legend(title="Legend"))

```


```{r}
arimax_year <- auto.arima(train_year, xreg = promo_train)
```


```{r}
checkresiduals(arimax_year)
accuracy(arimax_year)
arimax_year
```

```{r}
result_arimax_year <- forecast(arimax_year, xreg=c(), h = 10)
```

```{r}
result_arimax_year
```

```{r}
plot_start = 0
plot_end = 10
autoplot(test_year, series='train') +
  autolayer(ts(fitted(result_arimax_year)[plot_start:plot_end], start=2019 + 2/365, end=2019+10/365, frequency = 365),  series="fitted") + 
  xlab("day") +
  ylab("quantity") +
  ggtitle("Quantity of fresh fish seleed") +
  guides(colour=guide_legend(title="Legend"))

```








